supplement

### 2019-08-09 fig1_2app.Rmd
overview

>>>>

|competing| miRNA | Competing_expression | miRNA_expression | seed_type | region | energy
|-----------|------------|----------|----------------|---------|-----------|----------|
| `Gene1`   | `Mir1` | 10000 | 1000 | 0.43 | 0.30 | -20 |
| `Gene2`   | `Mir1` | 10000 | 1000 | 0.43 | 0.01 | -15 |
| `Gene3`   | `Mir1` | 5000  | 1000 | 0.32 | 0.40 | -14 |
| `Gene4`   | `Mir1` | 10000 | 1000 | 0.23 | 0.50 | -10 |
| `Gene4`   | `Mir2` | 10000 | 2000 | 0.35 | 0.90 | -12 |
| `Gene5`   | `Mir2` | 5000  | 2000 | 0.05 | 0.40 | -11 |
| `Gene6`   | `Mir2` | 10000 | 2000 | 0.01 | 0.80 | -25 |
